Standalone Tactics using OpenTheory

### 2012-02-13 paper.tex
some more minor tweaks

It makes sense to speak of similar proof tools in different interactive theorem provers not just because they implement essentially the same logic, but also because there is a shared base of concepts: booleans, inductive datatypes, recursive functions, natural numbers, lists, sets, etc.
The \OpenTheory standard library~\cite{hurd2011} formalises this shared base as a collection of theory packages containing proofs written in the simple \emph{article} format designed for storing and sharing higher order logic theories~\cite{hurd2009}.
We use \OpenTheory as a language for users of interactive theorem provers to communicate with proof tools on a remote server, and thereby obtain the following two benefits:
\begin{enumerate}
\item\textbf{Proof Articles:} A standard format to encode the goals that will be sent to the proof tools and the proofs that will be received.

@@

Requirement~\ref{req:log} poses the highest barrier: a standalone tactic must record a proof at a level of detail sufficient to prove the same theorem using the \OpenTheory kernel.
It helps if the system containing the tactic uses the LCF architecture, that is, theorems can only be created by a small number of primitive inference rules, as is the case for HOL4 and HOL Light.

@@

The sizes of the articles for the test goals and the resulting proofs are comparable to the typical size of web requests and the resulting pages, so we can be confident that we are within the normal operating range of the web tools we use (\texttt{curl} on the client and CGI scripts on the server). For standalone tactics generating large proofs we may wish to compress them using \texttt{gzip} before sending them to the client---previous experiments showed a 90\% compression ratio is typical on articles~\cite{hurd2009}.

As for the execution time, the bulk of the time is spent executing the standalone tactic on the web and communicating, so there is not much to be gained from optimizing the client.
``Web Time'' includes reading the goal article, running the proof tool, writing the proof article, and network communication.
Using \texttt{traceroute} we see a 0.173s network delay between the test client in Portland, OR, USA and the test server in Cambridge, UK, which accounts for at least 0.346s of delay.
The overall time is in the 1--2s range, which is very slow for workaday tactics but may well be tolerated by the user to gain access to the functionality of a proof tool on another system.

>>>>

It makes sense to speak of similar proof tools in different interactive theorem provers not just because they implement essentially the same logic, but also because there is a shared base of concepts: booleans, inductive datatypes, recursive functions, natural numbers, lists, sets, etc.
The \OpenTheory standard library~\cite{hurd2011} formalises this shared base as a collection of theory packages containing proofs written in the simple \emph{article} format designed for storing and sharing higher order logic theories~\cite{hurd2009}.
We use \OpenTheory as a language for interactive theorem provers to communicate with proof tools on a remote server, and thereby obtain the following two benefits:
\begin{enumerate}
\item\textbf{Proof Articles:} A standard format to encode the goals that will be sent to the proof tools and the proofs that will be received.

@@

Requirement~\ref{req:log} poses the highest barrier: a standalone tactic must record each proof at a level of detail sufficient to prove the same theorem using the \OpenTheory kernel.
It helps if the system containing the tactic uses the LCF architecture, that is, theorems can only be created by a small number of primitive inference rules, as is the case for HOL4 and HOL Light.

@@

The sizes of the articles for the test goals and the resulting proofs are comparable to the typical size of web requests and the resulting pages, so we can be confident that we are within the normal operating range of the web tools we use (\texttt{curl} on the client and CGI scripts on the server).
For problems involving larger articles (long proofs or big goals) we may wish to compress them using \texttt{gzip} before sending them to the client---previous experiments showed a 90\% compression ratio is typical on articles~\cite{hurd2009}.

Turning now to execution time, the bulk of the time is spent executing the standalone tactic on the web and communicating, so there is not much to be gained from optimizing the client.
``Web Time'' includes reading the goal article, running the proof tool, writing the proof article, and network communication.
Using \texttt{traceroute} we see a 0.173s network delay between the test client in Portland, OR, USA and the test server in Cambridge, UK, which accounts for at least 0.346s of delay.
The overall time is in the 1--2s range, which is very slow for workaday tactics but may well be tolerated by the user to gain access to the functionality of a proof tool on another system.
